Capitalized Title Here

### 2021-03-11 CMPSpaper_writing/CMPSpaper_writing.Rmd
edits through signature extraction

### Extracting signatures from LEAs

The automated framework  used in this paper was proposed by @aoas. In order to obtain bullet signatures from the x3p files of bullet land engravings, we use the `R` packages `x3ptools` [@x3ptools] and `bulletxtrctr` [@bulletxtrctr]. `x3ptools` \hh{is a package to read, write, and generally, process } x3p files. 
<!--In the case of Hamby set 252, we need to convert the measurements of x3p files from meters to microns (`x3ptools::x3p_m_to_mum`) and rotate x3p files to make the long axis horizontal (`x3ptools::x3p_rotate`).--> 
\hh{it's land **engraved** areas, not impressions (that was wrong in Eric's first paper). Impressions are marks from impacts, such as the hit of a hammer or the hit from the breech face. Engravings are scratch marks.}
\autoref{fig:process}(a) shows a \hh{rendering of a 3d scan of a } bullet land  engraved area. The raised portion of the surface \hh{on the left and right of the scan are parts of the adjacent groove engraved areas (GEAs)}, \hh{the middle area shows a land-engraved area (LEA) with well expressed} striation marks. The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land engraving.
\hh{The next section is at an awkward level of detail - there's lots of details, but without the parameter settings it is still not a reproducible description. Could you instead describe things conceptually, and then link to the code that does this particular image?}

\wj{The white horizontal line in \autoref{fig:process}(a) indicates this fixed height selected by an algorithm, and \autoref{fig:process}(b) shows the cross-sectional view of the bullet scan at this height. Then we can acquire the crosscut data (`ccdata`) of the scan at this height. \autoref{fig:process}(c) shows the typical pattern of the crosscut data, where "wedges" can be found on the left and right side and indicate the boundary between the land engraving and the groove engravings. The next step is to locate and chop these wedge areas so that only the data of the land engraving in the middle is kept (as shown in \autoref{fig:process}(d)). With the groove engravings excluded, we can then smooth out the land engraving curvature (\autoref{fig:process}(e)) using LOESS (locally estimated scatter plot smoothing) [@loess] and obtain the bullet signature (\autoref{fig:process}(f)). \autoref{fig:process} illustrates this framework. Sometimes the algorithm in our framework cannot determine the valid location of the crosscut or the grooves due to the deformation of a bullet, so we also developed a `R` Shiny App called `bulletinspectR` to identify and correct those errors. Note that NIST researchers used a different way of getting the bullet signatures in their paper [@cmps].}

>>>>

### Extracting signatures from LEA scans

The automated framework  used in this paper was proposed by @aoas. In order to obtain bullet signatures from the x3p files of bullet land engravings, we use the `R` packages `x3ptools` [@x3ptools] and `bulletxtrctr` [@bulletxtrctr]. `x3ptools` \hh{is a package to read, write, and generally, process } x3p files. 
<!--In the case of Hamby set 252, we need to convert the measurements of x3p files from meters to microns (`x3ptools::x3p_m_to_mum`) and rotate x3p files to make the long axis horizontal (`x3ptools::x3p_rotate`).--> 
<!--\hh{it's land **engraved** areas, not impressions (that was wrong in Eric's first paper). Impressions are marks from impacts, such as the hit of a hammer or the hit from the breech face. Engravings are scratch marks.}-->
\hh{\autoref{fig:process} gives an overview of all of the steps in the process from scan to signatures.}
\autoref{fig:process}(a) shows a \hh{rendering of a 3d scan of a } bullet land  engraved area. The raised portion of the surface \hh{on the left and right of the scan are parts of the adjacent groove engraved areas (GEAs)}, \hh{the middle area shows a land-engraved area (LEA) with well expressed} striation marks. The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land engraving.
<!--\hh{The next section is at an awkward level of detail - there's lots of details, but without the parameter settings it is still not a reproducible description. Could you instead describe things conceptually, and then link to the code that does this particular image?} -->
The white horizontal line in \autoref{fig:process}(a) indicates which cross-section was identified by the algorithm to represent the LEA; \autoref{fig:process}(b) shows the corresponding cross-sectional view. <!--Then we can acquire the crosscut data (`ccdata`) of the scan at this height. --> \hh{XXX passive voice for things that are not part of this paper :)}
Groove engraved areas are removed from the analysis as indicated by the vertical blue lines in \autoref{fig:process}(c) and \autoref{fig:process}(d)). A non-parametric LOESS smooth  [@loess] is fit to capture the bullet curvature (\autoref{fig:process}(e)) and, finally, the **bullet signature** (\autoref{fig:process}(f)) is obtained as residuals of the cross-section and the fitted smooth. 
\hh{Identifiying the groove engraved areas correctly is fundamental for a correct down-stream analysis of the signatures. To allow for a human-in-the middle inspection and intervention we have provided an interactive web-application, implemented as `R` Shiny App [@shiny],}   `bulletinspectR` to identify and correct those errors. 
\hh{An example of the extraction process with corresponding code and parameter settings can be found at XXX.}
Note that \hh{the process of extracting signatures might be different from the one used in @cmps because no code or parameter settings are made available publicly.}
